### 2016-07-12 Docs/managing_jobs/managingjobs.tex
update edison yt directions

The scripts {\tt parallel-yt} and {\tt process-edison.run} in {\tt
Util/job\_scripts/edison} show how to invoke \yt\ to loop over a 
series of plotfiles and do visualization.  A number of tasks are
run at once on the node, each operating on a separate file.  Note:
it is important that {\tt aprun} be used to launch the \yt\ script
to ensure that it is run on the compute node.

>>>>

The scripts {\tt parallel-yt} and {\tt process-edison.slurm} in {\tt
  Util/job\_scripts/edison} show how to invoke \yt\ to loop over a
series of plotfiles and do visualization.  A number of tasks are run
at once on the node, each operating on a separate file.  The {\tt
  parallel-yt} script then calls {\tt vol.py} to do the volume
rendering with \yt.  Note: it is important that {\tt srun} be used to
launch the \yt\ script to ensure that it is run on the compute node.

A simple {\tt test-yt.slurm} script shows how to just call the
\yt\ python script directly, using one node and 24 threads, again
using {\tt srun} to execute on the compute node.
